### 2012-11-27 paper.tex
structure outlined

\documentclass{article}

\begin{document}

\title{Implementation Design Patters for Pursuit-Evasion Problems with Bounded Speed}
\author{Daniel Savage\\CSC 426\\{V00701453}}
\date{November 2012}
\maketitle
\pagebreak

\section{Introduction}
Hello World!

\section{Paradigm 1 - Discrete Formulation}
Hello World!

\section{Paradigm 2 - Formulation on the Continuous Plane}
Hello World!

\section{Blended Paradigm Concept}
Hello World!

\section{Conclusion}
Hello World!

\end{document}

### 2012-11-29 paper.tex
Intro skeleton
Switching machines
paradigm 1 outline

@@
 \section{Introduction}
-Hello World!
+-- Explanation of pursuit-evasion problem in general.
+-- The two various methods for analyzing the problem
+-- a solution for blending the two solutions together
 
 \section{Paradigm 1 - Discrete Formulation}
-Hello World!
+-- explanation of the paradigm
+-- mathematical definitions
+-- planar graphs need max three pursuers
 

### 2012-11-30 paper.tex
filled out skeleton
(woo)
mostly done discrete formulation

--- 2012-11-27 paper.tex
@@
 \documentclass{article}
+
+\usepackage{amsmath}
+
+\linespread{1.3}
 
@@
 \title{Implementation Design Patters for Pursuit-Evasion Problems with Bounded Speed}
-\author{Daniel Savage\\CSC 426\\{V00701453}}
+\author{Daniel Savage\\CSC 426\\{V00701453}\\savaged@uvic.ca}
 \date{November 2012}
@@
 \section{Introduction}
-Hello World!
+% Explanation of pursuit-evasion problem in general.
+% The two various methods for analyzing the problem
+% a solution for blending the two solutions together
 
 \section{Paradigm 1 - Discrete Formulation}
-Hello World!
+The Discrete Formulation of Pursuit-Evasion studies focus on recognizing scenarios in a set of states on a connected graph.
+This creates a paradigm where strategies are much more easily recognized and explained.
+Routes and movements are generalized and win/lose situations for pursuers and evaders can often be predicted ahead of time by the nature of the graph played on.
+
+Let the environment that the pursuers and evaders coexist in be a finite, connected graph \(G\).
+Let \(G\)'s vertices be represented as \(v_1,v_2,...,v_n\), each being a distinct location in the environment.
+All edges are considered to be undirected and of equal length.
+Let the set of all \(q\) pursuers in \(G\) can be represented as \(P = {p_1,...,p_q}\), with each being on some \(v_i\) in \(G\).
+Subsequently, also let the set of all \(w\) evaders in \(G\) can be represented as \(E = {e_1,...,e_w}\), with each being on some \(v_i\) in \(G\).
+Any vertex in \(G\) can be occupied by more than one pursuer and/or evader.
+
+In the Discrete Formulation of Pursuit-Evasion problems, scenarios are usually played to the following rules: \(P\) and \(R\) occupy some vertex of \(G\).
+Subsequently each alternates moving from one adjacent node to another.
+This alternation can be from one member of each at a time, or all of one's and then another's.
+The pursuers win the scenario if they are able to "catch" each evader by occupying the same vertex.
+Evader(s) do not all need to be caught in the same turn.
+Alternatively, the evader(s) win if at least one of them can evade the pursuer(s) indefinitely.\cite{copsRobbers}
+
+There can be varieties on each of the rules for this scenario.
+The Pursuer(s) and/or evader(s) may not need to necessarily move each turn, which can sometimes determine whether or not one side wins or loses.
+Also the pursuer(s) or evader(s) may not have perfect information when making decisions, only able to "see" others at certain distances.
+If pursuers do not know any information other than the node they occupy, we can often represent these scenarios as search games.
+\cite{parsons}
+
+Provided that \(G\) is a planar graph, we can make the assumption that we will only need at most three pursuers to catch all evaders. \cite{copsRobbers} We can show this with the following algorithm:
 
 \section{Paradigm 2 - Formulation on the Continuous Plane}
-Hello World!
+% explanation of the paradigm
+% mathematical definitions and/or data structures
+% general setup and rules of "play"
+% visibility polygons and gap management
+% area contamination and management
+% NP-hardness
 
 \section{Blended Paradigm Concept}
-Hello World!
+% explanation of the paradigm (NP-hardness aleviation)
+% mathematical definitions and/or data structures
+% general setup and rules of "play"
+% delunay triangulation and minimum spanning tree connection
+% visibility and contamination representation
+% tesslation through barycenters
+% strategic issues
 
 \section{Conclusion}
-Hello World!
+% no idea what you're goona write here
+
+\section{References}
+
+\begin{thebibliography}{9}
+
+\bibitem{copsRobbers}
+  M. Aigner and M. Fromme,
+  \emph{A Game of Cops and Robbers}.
+  Math. Institut, Freie Universitat Berlin,
+  Discrete Applied Mathematics, Volume 8, Issue 4,
+  1984
+
+\bibitem{parsons}
+  T.D. Parsons,
+  \emph{Pursuit-Evasion in a Graph}.
+  The Pennsylvania State University
+  Theory and Applications of Graphs, Volume 642, pp 426-441
+  1978
+
+\end{thebibliography}
 

### 2012-11-30 paper.tex
finalized discrete formulation

@@
 \usepackage{amsmath}
+\usepackage{algorithm2e}
 
@@
 
-Provided that \(G\) is a planar graph, we can make the assumption that we will only need at most three pursuers to catch all evaders. \cite{copsRobbers} We can show this with the following algorithm:
+Provided that \(G\) is a planar graph, we can make the assumption that we will only need at most three pursuers to catch all evaders, as proven by Aigner and Fromme.
+This is performed by one to three pursuers sequentially closing off the region occupied by an evader, tackling each one at a time.
+One pursuer is able to step into the area where the evader is free to move, and its cohorts (if any) are able to cover its congruent spaces, taking advantage of the planar properties of the graph.
+This is repeated until each evader is caught.
+\cite{copsRobbers}
 

### 2012-11-30 paper.tex
addeded basic continuous formation

@@
 \usepackage{amsmath}
+\usepackage{amsfonts}
 \usepackage{algorithm2e}
@@
 \section{Paradigm 2 - Formulation on the Continuous Plane}
-% explanation of the paradigm
+Whilst the Discrete Formulation offers a powerful strategic methodology, it does not sadly reflect a realistic situation very well for a group of pursuers.
+Movements are not made in instantaneous, distinguishable jumps in reality, nor is Pursuit-Evasion generally a perfect-information game.
+Formulation on a Continuous Plane, or Continuous Formulation, is the idea behind expressing a Pursuit-Evasion scenario as a geometric real-world model.
+Concepts for applications of this model often include teams of robots searching for people in an enclosed space.
+
 % mathematical definitions and/or data structures
-% general setup and rules of "play"
-% visibility polygons and gap management
-% area contamination and management
-% NP-hardness
+To start, we will begin by defining the scenario environment as an open set \(R\subset\mathbb{R}^2\).
+\(R\) is to be a simply-connected and has some sort of polygonal boundary.
+Some scenarios define that \(R\) has holes.
+\(P\subset R\) is assumed to be the set of points that represent the locations of the various pursuers of the scenario.
+Accordingly \(E\subset R\) is assumed to make up the set of evaders, their locations being represented as points as well.
+Members of \(P\) has perfect information about their location with respect to \(R\) and each other, but not necessarily \(E\).
+Both pursuers and evaders move at various speeds within \(R\).
+Members of \(P\) generally are expected to move at a bounded consistent speed \(V_P\), while evaders can be viewed as having either a bounded speed or in some cases, unbounded.
+\cite{limVis, robotics} Pursuers are generally considered to have "caught" the evaders when being within a certain distance of them.
+
+As stated previously, the set of pursuers \(P\) do not have perfect information of \(R\) and can only see a combined limited region at one time.
+Subsequently, they may not know where the evaders \(E\) are located.
+This visible region is known as the \emph{visibility polygon} \(V\).
+\(V\) is composed of a collection of line segments that may partially align with \(R\)'s shape itself.
+It's assumed \(V\)'s topology changes changes as it's corresponding \(P\) moves about \(R\).
+The line segments of \(V\) are that cross across the face of \(R\)'s polygonal shape are known as \emph{gap edges}.
+These gap edges allow us to divide \(R\) into shrinking and growing regions of visibility.
+\cite{limVis, robotics}
+
+To map probability of where evaders may be in \(R\), regions currently not visible are given a status of either \emph{contaminated} or \emph{uncontaminated}.
+A contaminated space represents the idea that an evader may be hiding within it, and the pursuer(s) can not be certain that the area has been completely checked.
+When gap edges shrink and change position, regions can split and merge together.
+If a contaminated region merges with an uncontaminated region, the area is said to be \emph{recontaminated} and needs to be re-checked by the pursuer(s).
+This is to account for evaders potentially moving from one area outside of \(V\) to another.
 
@@
 
+\bibitem{robotics}
+  Benjamin Tovar and Steven M. LaValle,
+  \emph{Visibility-based Pursuit-Evasion with Bounded Speed}.
+  Department of Computer Science, University of Illinois,
+  The International Journal of Robotics Research 2008 27: 1350,
+  2008
+
+\bibitem{limVis}
+  Brian P. Gerkey and Sebastian Thrun and Geoff Gordon,
+  \emph{Visibility-based Pursuit-Evasion with limited field of view}.
+  Artificial Intelligence Lab, Stanford University,
+  The National Conference on Artificial Intelligence 2004,
+  2004
+
 \end{thebibliography}

### 2012-11-30 paper.tex
compiled PDF images
further work; genereal commit

@@
 \usepackage{algorithm2e}
+\usepackage{graphicx}
+\usepackage[font={small,it}]{caption}
+
+\graphicspath{{./gfx/}}
 
@@
 
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.4\textwidth]{"graph1"}
+\caption{An example of a Discrete Formulation on a closed graph; evaders and pursuers are marked accordingly as \(P_1,P_2,E_1,E_2,E_3\)}
+\end{figure}
+
 Let the environment that the pursuers and evaders coexist in be a finite, connected graph \(G\).
@@
 Any vertex in \(G\) can be occupied by more than one pursuer and/or evader.
+
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.7\textwidth]{"graph2_steps"}
+\caption{An example scenario on a graph with three steps where the pursuer wins.
+Note that in this example the evader \(E_1\) must move each turn.
+If \(E_1\) is able to "stay put" on a turn it can evade \(P_1\) indefinitely}
+\end{figure}
 
@@
 
-% mathematical definitions and/or data structures
 To start, we will begin by defining the scenario environment as an open set \(R\subset\mathbb{R}^2\).
@@
 % explanation of the paradigm (NP-hardness aleviation)
+The aim of this section is to present a paradigm that attempts to combine both advantages of the Discrete and Continuous Formulations for pursuers in a real-time environment.
+We'll refer to this as the \emph{Blended Paradigm} from now on.
+The Blended Paradigm works on the idea of having a Discrete Formulation model stored, and update it's state according to observed stimuli found in the Continuous Formulation.
+Subsequently we make strategic decisions for pursuers in the Discrete Model, and execute them in the Continuous Formulation.
+This allows us to take advantage of the Discrete Formulation's simplified structure and the Continuous Formulation's real-life applications.
+
 % mathematical definitions and/or data structures
-% general setup and rules of "play"
+To start, we will begin by defining the scenario environment as an open set \(R\subset\mathbb{R}^2\).
+\(R\) is to be a simply-connected and has some sort of polygonal boundary.
+Let sets \(P,E\subset{R}\) be the positions of the pursuers and evaders and their velocities identical to that found in the Continuous Formulation.
+Let \(G\) be an undirected, weighted-edge graph representing \(R\), with each of its vertex in a state being either \emph{visible, uncontaminated,} or \emph{contaminated}.
+Later in this section we will explain how \(G\) represents \(R\).
+Each pursuer and evader will keep track of which vertex it currently "occupies".
+It is also assumed that all pursuers in \(P\) know their location relative to \(R\).
+
 % delunay triangulation and minimum spanning tree connection
-% visibility and contamination representation
+To have \(G\) represent \(R\), we take advantage of \(R\)'s shape being a closed polygon.
+By performing, a Delaunay Triangulation on \(R\), we acquire a triangulation composed of \(R\)'s vertices.
+\cite{dTri} It is assumed that the triangles outside of \(R\) are "stripped" and discarded immediately.
+We are left with a set of adjacent triangles that make up \(R\).
+For each triangle, add a corresponding vertex to \(G\) and add an edge between each adjacent triangle.
+The weight of an edge between two triangle's vertices is the distance between each triangle's midpoint in barycentric coordinates.
+\cite{bCenter} \(G\) now represents a set of general areas in \(R\) and the approximate distances between each.
+
+%sexy diagram
+
+A running scenario for the Blended Paradigm looks incredibly similar to the Continuous Formulation.
+The main difference is that instead of managing sets of changing visibility polygons, visibility is generalized into triangular sections which are managed in \(G\).
+Let is be assumed for a pursuer to "catch" an evader, they must both be inside the same triangulated region.
+In real-time, a pursuer checks at each moment which triangulated regions it can completely see.
+If a region can be completely seen in \(R\) it is marked as visible in \(G\).
+A triangulated region that was once visible in \(R\) but subsequently no longer is considered uncontaminated.
+Regions that have never been visible are considered contaminated.
+
+Contaminated triangles and vertices in \(G\) are meant to represent regions in \(R\) where an evader could possibly be.
+In that case, if a contaminated region is adjacent to an uncontaminated region, it is possible that an evader could move from the contaminated to the uncontaminated region, making both uncontaminated.
+This creates a degree of "spreading" contamination that needs to be kept in check by the pursuers.
+Since the evaders move at a bounded speed though, it can be expected that contamination does not happen necessarily instantaneously.
+For this reason the edges in \(G\) have a weight associated with them.
+Contamination from one vertex/triangle to another happens at a speed: \begin{displaymath}
+foo penis
+\end{displaymath}
+
 % tesslation through barycenters
@@
 \begin{thebibliography}{9}
+
+\bibitem{dTri}
+  \emph{Delaunay Triangulation},
+  Wolfram Mathworld,
+  Retrieved November 2012
+
+\bibitem{bCenter}
+  \emph{Barycentric Coordinates},
+  Wolfram Mathworld,
+  Retrieved November 2012
 

### 2012-12-01 paper.tex
explanation of blended paradigm
rushing this so hard

@@
 For this reason the edges in \(G\) have a weight associated with them.
-Contamination from one vertex/triangle to another happens at a speed: \begin{displaymath}
-foo penis
-\end{displaymath}
+Contamination from one vertex/triangle to another happens after a delay \(D\) where: \begin{displaymath}
+D = \frac{\text{length of edge between vertices}}{\text{maximum bounded speed of evader(s)}}\times \text{S} ; S\in(0,1]
+\end{displaymath}\(S\) represents a "shortcut" value, which can be altered to scale contamination speed/ Evaders may not necessarily go from center to center in each triangle, and could spend less time in one than expected.
 
-% tesslation through barycenters
-% strategic issues
+An issue that may arise is evader travel time in a triangle/vertex may be less than the estimated contamination delay.
+An evader may only spend a moment crossing a corner of a triangle and jump ahead of the spreading contamination, for example.
+To help alleviate this error ahead of time, one can subdivide a triangle/vertex into three at it's barycentric center.
+This technique divides areas into smaller regions with faster contamination speeds, allowing for a granularity closer to \(\mathbb{R}^2\).
+
+Strategically, pursuers can follow various techniques to capture evaders in \(R\).
+The first to come to mind is attempting to clear all contaminated spaces.
+This may be possible in some graphs, but others could have contamination that spreads faster than it can be removed.
+Another process is to use the theorem provided by Aigner and Fromme, if three pursuers move along the triangles akin to \(G\), slowly closing in on a potential area, they can encapsulate and close any evader in theory.
+We can apply this theorem due to the collection of triangles being planar and reflecting onto \(G\).
+This method would be irrespective of visibility if all pursuers begin in one "corner" of the polygon.
 

### 2012-12-01 paper.tex
added some diagrams
completed diagrams

@@
 
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.7\textwidth]{"visPoly"}
+\caption{A pursuer P in an example R.
+The visibility polygon for P is shaded in showing the area P can view.
+Note the edge gaps that bound the visibility polygon and the rest of R.
+If P were to move as far to the right as possible, the visible area near to the top of R would vanish.}
+\end{figure}
+
 As stated previously, the set of pursuers \(P\) do not have perfect information of \(R\) and can only see a combined limited region at one time.
@@
 
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.7\textwidth]{"trangulation"}
+\caption{A diagram showing the process for deriving \(G\) from \(R\).
+In (1) the initial environment is visible.
+Subsequently it is triangulated using Delaunay Triangulation in (2).
+Finally, adjacent triangles are used to construct the edges and nodes for \(G\) in (3).}
+\end{figure}
+
 % delunay triangulation and minimum spanning tree connection
@@
 
-%sexy diagram
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.7\textwidth]{"visibility"}
+\caption{A diagram showing \(R\) divided into triangles according to \(G\) and the visibility according to various pursuer locations.
+Note that visibility is not a function of which triangle/vertex in \(G\) the pursuer is located in.}
+\end{figure}
 
@@
 Regions that have never been visible are considered contaminated.
+
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.7\textwidth]{"contamination"}
+\caption{A diagram showing \(R\) with a contamination spreading from the right.
+Note that the contamination does not necessarily spread at the closest path in the euclidean plane and would require smaller triangles.}
+\end{figure}
 
@@
 
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.7\textwidth]{"tesslation"}
+\caption{A diagram showing \(R\) with its triangles subdivided into smaller triangles.
+Note the population of \(G\) has multiplied by 3.
+If this were to be continued the triangles would likely be indistinguishable from \(\mathbb{R}^2\).}
+\end{figure}
+
 An issue that may arise is evader travel time in a triangle/vertex may be less than the estimated contamination delay.
@@
 This technique divides areas into smaller regions with faster contamination speeds, allowing for a granularity closer to \(\mathbb{R}^2\).
+It's important to keep note that \(G\) still keeps its planar status even when subdivided.
 
@@
 % no idea what you're goona write here
-
-\section{References}
 

### 2012-12-01 paper.tex
introduction and conclusion

@@
 \section{Introduction}
-% Explanation of pursuit-evasion problem in general.
-% The two various methods for analyzing the problem
-% a solution for blending the two solutions together
+Consider the award-winning board game \emph{Scotland Yard} by Milton-Bradley.
+The concept of the game is for a team of five detectives to track down the nefarious Mr.X in downtown London.
+Each player takes turns moving a pawn from intersection to intersection across London, attempting to corner Mr.X.
+Mr.X, while outnumbered, is not entirely visible to the players at all times.
+The detectives win if they can land on the same intersection as Mr.X within a set number of turns, otherwise Mr.X is crowned victor.
+
+Scotland Yard would be considered by most mathematicians and computer scientists to be a pursuit-evasion game.
+Pursuit-Evasion games and problems can vary from paradigm to paradigm, but all follow the same basic scenario: one or more members of one group attempt to track down one or more members of another group in some environment.
+Examples of this often include firefighters looking for people in a building, or search-and-rescue teams looking for people lost in caves.
+\cite{parsons, robotics}
+
+Two common methods, or \emph{formulations} are used usually to represent a Pursuit-Evasion scenario: the \emph{Discrete Formulation} and the \emph{Formulation on a Continuous Plane}.
+The Discrete Formulation follows the concept of interpreting the scenario as moving players on a graph, much like the Scotland Yard game.
+Formulation on the Continuous Plane follows the idea of modeling pursuers and evaders in a geometric, real-time scenario.
+
+Throughout this paper we will examine the two paradigms in more depth and note their characteristics.
+Subsequently, we will then propose a pursuit-evasion strategy for applying Discrete techniques in a Continuous real-time environment.
 
@@
 \section{Conclusion}
-% no idea what you're goona write here
+In this paper we have reviewed the most recognized concepts Pursuit-Evasion and examined certain parts of their characteristics.
+Subsequently, we then presented a combination of their strategies to allow for a real-time, geometric paradigm of the problem that allows for discrete strategies to be applied.
+While we did not have the time or resources to implement this solution in real-time, we have ground to believe that this solution would work in an unbounded speed case with the right strategies in place.
 

### 2012-12-01 paper.tex
added quick abstract

@@
 \pagebreak
+
+\begin{abstract}
+In this paper we give an overview of Discrete and Continuous Pursuit-Evasion problems, explaining their methodologies, information structures, and play scenarios.
+Subsequently, we attempt to combine their qualities together to create a real-time solution with Discrete strategic techniques.
+\end{abstract}
 

### 2012-12-01 paper.tex
fixed some typos

@@
 \section{Paradigm 1 - Discrete Formulation}
-The Discrete Formulation of Pursuit-Evasion studies focus on recognizing scenarios in a set of states on a connected graph.
+The Discrete Formulation of Pursuit-Evasion studies focuses on recognizing scenarios in a set of states on a connected graph.
 This creates a paradigm where strategies are much more easily recognized and explained.
@@
 All edges are considered to be undirected and of equal length.
-Let the set of all \(q\) pursuers in \(G\) can be represented as \(P = {p_1,...,p_q}\), with each being on some \(v_i\) in \(G\).
-Subsequently, also let the set of all \(w\) evaders in \(G\) can be represented as \(E = {e_1,...,e_w}\), with each being on some \(v_i\) in \(G\).
+Let the set of all \(q\) pursuers in \(G\) be represented as \(P = {p_1,...,p_q}\), with each being on some \(v_i\) in \(G\).
+Also let the set of all \(w\) evaders in \(G\) be represented as \(E = {e_1,...,e_w}\), with each being on some \(v_i\) in \(G\).
 Any vertex in \(G\) can be occupied by more than one pursuer and/or evader.
@@
 
-There can be varieties on each of the rules for this scenario.
+There can be variations on each of the rules for this scenario.
 The Pursuer(s) and/or evader(s) may not need to necessarily move each turn, which can sometimes determine whether or not one side wins or loses.
@@
 To start, we will begin by defining the scenario environment as an open set \(R\subset\mathbb{R}^2\).
-\(R\) is to be a simply-connected and has some sort of polygonal boundary.
+\(R\) is simply-connected and has some sort of polygonal boundary.
 Some scenarios define that \(R\) has holes.
@@
 Accordingly \(E\subset R\) is assumed to make up the set of evaders, their locations being represented as points as well.
-Members of \(P\) has perfect information about their location with respect to \(R\) and each other, but not necessarily \(E\).
+Members of \(P\) have perfect information about their location with respect to \(R\) and each other, but not necessarily \(E\).
 Both pursuers and evaders move at various speeds within \(R\).
@@
 \caption{A pursuer P in an example R.
-The visibility polygon for P is shaded in showing the area P can view.
+The visibility polygon for P is shaded, showing the area P can view.
 Note the edge gaps that bound the visibility polygon and the rest of R.
@@
 
-As stated previously, the set of pursuers \(P\) do not have perfect information of \(R\) and can only see a combined limited region at one time.
+As stated previously, the set of pursuers \(P\) do not have perfect information of \(R\)'s contents and can only see a combined limited region at one time.
 Subsequently, they may not know where the evaders \(E\) are located.
@@
 It's assumed \(V\)'s topology changes changes as it's corresponding \(P\) moves about \(R\).
-The line segments of \(V\) are that cross across the face of \(R\)'s polygonal shape are known as \emph{gap edges}.
+The line segments of \(V\) that cross across the face of \(R\)'s polygonal shape are known as \emph{gap edges}.
 These gap edges allow us to divide \(R\) into shrinking and growing regions of visibility.
@@
 To start, we will begin by defining the scenario environment as an open set \(R\subset\mathbb{R}^2\).
-\(R\) is to be a simply-connected and has some sort of polygonal boundary.
-Let sets \(P,E\subset{R}\) be the positions of the pursuers and evaders and their velocities identical to that found in the Continuous Formulation.
+\(R\) is to be simply-connected and has some sort of polygonal boundary.
+Let sets \(P,E\subset{R}\) be the positions of the pursuers and evaders and their velocities identical to those found in the Continuous Formulation.
 Let \(G\) be an undirected, weighted-edge graph representing \(R\), with each of its vertex in a state being either \emph{visible, uncontaminated,} or \emph{contaminated}.
@@
 To have \(G\) represent \(R\), we take advantage of \(R\)'s shape being a closed polygon.
-By performing, a Delaunay Triangulation on \(R\), we acquire a triangulation composed of \(R\)'s vertices.
+By performing a Delaunay Triangulation on \(R\), we acquire a triangulation composed of \(R\)'s vertices.
 \cite{dTri} It is assumed that the triangles outside of \(R\) are "stripped" and discarded immediately.
@@
 Contaminated triangles and vertices in \(G\) are meant to represent regions in \(R\) where an evader could possibly be.
-In that case, if a contaminated region is adjacent to an uncontaminated region, it is possible that an evader could move from the contaminated to the uncontaminated region, making both uncontaminated.
+In that case, if a contaminated region is adjacent to an uncontaminated region, it is possible that an evader could move from the contaminated to the uncontaminated region, making both contaminated.
 This creates a degree of "spreading" contamination that needs to be kept in check by the pursuers.
